Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-08-31 reanalysis-5-outcome_analysis.qmd
reanalysis out ome model update

```{r define-formula}
# Get the ORIGINAL formulas from functions.R
# Using original to maintain consistency with submitted analysis
original_formulas <- get_analysis_formulas()

# Use the full formula (without dr_severity)
main_effects_formula <- original_formulas$full
```

@@

**Model Structure:**
- Main effect of interest: `ever_lapse_binary`
- Adjustment variables: DR severity, treatment status, and baseline covariates
- No interaction terms

>>>>

```{r define-formula}
# Get the REANALYSIS formulas from functions.R
# Using reanalysis formulas that include dr_severity as a covariate
reanalysis_formulas <- get_analysis_formulas_reanalysis()

# Use the full formula with dr_severity
main_effects_formula <- reanalysis_formulas$full
```

@@

**Model Structure:**
- Main effect of interest: `ever_lapse_binary`
- Adjustment variables: 
  - DR severity (`dr_severity`)
  - Baseline visual acuity (`baseline_VA_logMAR`)
  - Demographics and comorbidities
  - Treatment indicators
- No interaction terms
